The truncated KdV framework for modeling anomalous waves induced by abrupt depth changes

### 2019-07-22 WavesData-2019/LatexNotes/notes.tex
NM

>>>>

\np
%----------------------------------------------------------%
% Misc
%----------------------------------------------------------%
\section{Misc}
\subsection{The optimizer of the Hamiltonian is a traveling wave solution}
For the acceptance-rejection algorithm, it is important to find the maximal value of the Hamiltonian subject to the constraints of fixed energy $E = E_0$ and zero momentum $M = 0$. For simplicity, consider the KdV equation
\begin{equation}
\label{KdVsimple}
u_t + u u_x + \mu u_{xxx} = 0
\end{equation}
with corresponding Hamiltonian
\begin{equation}
H = \frac{1}{6} \int u^3 dx - \frac{\mu}{2} \int u_x^2 dx
\end{equation}

Consider the functional
\begin{equation}
F[u] = H[u] + \lambda_1 (E-E_0) + \lambda_2 (M-0)
\end{equation}
where $\lambda_1$ and $\lambda_2$ are Lagrangian multipliers. Taking the variational derivative gives
\begin{equation}
\frac{\delta F}{\delta u} = \frac{1}{2} u^2 + \mu u_{xx} + \lambda_1 u + \lambda_2 = 0
\end{equation}
which is a second-order nonlinear ODE for the optimizer $u = U(x)$. Note that this is identical to the condition for a traveling wave solution!!! To see this, consider traveling wave solutions of \ref{KdVsimple}, $u(x,t) = U(x-Vt)$. Inserting into \ref{KdVsimple} and integrating once gives
\begin{equation}
\frac{1}{2} U^2 + \mu U'' - V U = \text{Const}
\end{equation}
which is exactly the same condition!!!
